%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% File jslectureplanner.tex
%%
%% Manual of the jslectureplanner bundle.
%%
%% This file is part of the jslectureplanner bundle.
%%
%% Author: Juergen Spitzmueller <juergen.spitzmueller@univie.ac.at>
%%
%% This work may be distributed and/or modified under the
%% conditions of the LaTeX Project Public License, either version 1.3
%% of this license or (at your option) any later version.
%% The latest version of this license is in
%%   http://www.latex-project.org/lppl.txt
%% and version 1.3 or later is part of all distributions of LaTeX
%% version 2003/12/01 or later.
%%
%% This work has the LPPL maintenance status "maintained".
%% 
%% The Current Maintainer of this work is Juergen Spitzmueller.
%%
%% Code repository and issue tracker: https://github.com/jspitz/jslectureplanner
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[english]{article}

\usepackage[osf]{libertine}
\usepackage[scaled=0.7]{beramono}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{url}

% markup
\newcommand*\jmacro[1]{\textbf{\texttt{#1}}}
\newcommand*\jcsmacro[1]{\jmacro{\textbackslash{#1}}}
\newcommand*\joption[1]{\textbf{\texttt{#1}}}
\newcommand*\jfmacro[1]{\texttt{#1}}
\newcommand*\jfcsmacro[1]{\jfmacro{\textbackslash{#1}}}

% macros
\newcommand*\jslp{\textsf{jslectureplanner}}
\newcommand*\jsmt{\textsf{jsmembertable}}

% improve layout
\tolerance 1414
\hbadness 1414
\emergencystretch 1.5em
\hfuzz 0.3pt
\widowpenalty = 10000
\vfuzz \hfuzz
\raggedbottom

\usepackage{microtype}

\usepackage{babel}

\usepackage{listings}
\lstset{language={[LaTeX]TeX},
        basicstyle={\small\ttfamily},
        frame=single}

\setcounter{tocdepth}{2}

\begin{document}

\title{The \jslp\ bundle}

\author{Jürgen Spitzmüller%
\thanks{Please report issues via \protect\url{https://github.com/jspitz/jslectureplanner}.}}

\date{Version 1.5, 2017/03/12}

\maketitle

\begin{abstract}
\noindent The \jslp\ bundle provides a collection of packages
I have written in order to facilitate, and somewhat systematize,
the planning of my university courses and the generation of course material
(and thus, ultimately, to relieve me from some of the more boring and
time-consuming part of teaching work).
Currently, the bundle consists of the main, title-giving package \jslp\
that provides an interface to central, partly dynamically generated course
metadata as well as routines to generate programs, bibliographies etc., and one
smaller companion package: \jsmt, a package that can construct course
member and presence tables. This manual documents these packages.
\end{abstract}

\tableofcontents

\clearpage

\part{The \jslp\ package}

This part of the manual describes the basic user interface of the
\jslp\ package.
Please also refer to the example files included in the bundle in order to
see how \jslp\ is supposed to be used ``in practice''.

\section{Aim of this package}

The basic idea of the \jslp\ package is that you record
all general data of a course (date, semester, type, course title, session titles,
general information etc.) in a central tex file and then input this
file to all documents related to the course (such as the course program,
bibliography, scripts, handouts, beamer presentations, exercises etc.),
in order to re-use the recorded data.
This is particularly helpful if you have standard courses which
are held every other semester: instead of changing the data in every
single file, you just need to change it once, in the metadata file.

To further facilitate the planning, the \jslp\ package
is able to calculate the session dates of a whole semester, if the sessions
of the course follow at regular intervals.
You only need to set the date of the first session, the package does
the rest. Moreover, the package can be used to generate a sectioned
bibliography for the course via \textsf{biblatex}.

Since the package has been written for my own needs, it is somewhat tied
to my workflow. Particularly, it is tied to my context: teaching in
the Humanities at a German-speaking university. Hence, the categorization
of the package draws on this context. In particular, all default strings and
formats are German. However, it is possible to add new categories as
well as to customize and translate the strings.
This is described later in this manual.

\section{Requirements of \jslp}\label{sec:req-jslp}

The following packages are required and loaded by \jslp:
\begin{itemize}
 \setlength\itemsep{2pt}
 \item \textsf{calc}
 \item \textsf{datetime2}
 \item \textsf{etoolbox}
 \item \textsf{ifthen}
 \item \textsf{xkeyval}
\end{itemize}
\pagebreak

\section{General idea}

The general idea goes as follows:
\begin{itemize}
\item Set up a \emph{metadata.tex} file (or whatever name you prefer) and
record all meta information of the course in it (as described in sec.~\ref{sec:course-metadata}
and \ref{sec:lecplan}).
\item In your documents, load the package (\jcsmacro{usepackage\{jslectureplanner\}})
and/or%
\footnote{If you prefer to record the data via package options
(see sec.~\ref{sub:package-options}) instead of macros (see sec.~\ref{sec:via-macros}),
you need to load the package in the metadata file itself.}
 input the metadata file (\jcsmacro{input\{metadata.tex\}}).
\item Finally, use the macros described in sec.~\ref{sec:general-course-info}
and \ref{sec:session-specific-info} to retrieve the respective data and re-use
the recorded information in your documents.
\end{itemize}
The procedure is detailed in the following sections.


\section{Setting up course metadata\label{sec:course-metadata}}

You can set up the course metadata either via package options (if
you load the package in the metadata file; see sec.~\ref{sub:package-options})
or via specific macros (see sec.~\ref{sec:via-macros}).


\subsection{Via package options\label{sub:package-options}}

\jcsmacro{usepackage[<comma-separated options>]\{jslectureplanner\}}

\subsubsection{Course classification\label{sec:lecture-classification}}

The default course classification draws on the conventions at German-speaking
universities (or those where I have worked, for that matter). Each type is
connected to a verbose string (such as \emph{Seminar}), a short form (such as
\emph{SE}) and a form that is used to denote individual sessions (as
in ``the second \emph{session} of this course'').
\begin{description}
\item [\joption{type=<type>}] defines the course type. Predefined values are:

\begin{itemize}
\item \joption{vl}: A lecture (verbose form: \emph{Vorlesung}, short form:
      \emph{VL}, session form: \emph{Vorlesung})
\item \joption{ps}: Undergraduate seminar (verbose form: \emph{Proseminar},
      short form: \emph{PS}, session form: \emph{Sitzung})
\item \joption{se}: Seminar (verbose form: \emph{Seminar}, short form:
      \emph{SE}, session form: \emph{Sitzung})
\item \joption{ue}: Practical course (verbose form: \emph{Übung}, short
      form: \emph{UE}, session form: \emph{Sitzung})
\item \joption{ko}: Colloquium (verbose form: \emph{Kolloquium}, short form:
      \emph{KO}, session form: \emph{Sitzung})
\item \joption{pv}: Research seminar (verbose form: \emph{Privatissimum},
      short form: \emph{PV}, session form: \emph{Sitzung})
\end{itemize}

Section~\ref{sec:customizing-strings} explains how to extend this list and how
to customize the strings.
Please also cf. sec.~\ref{sec:styles} on the concept of ``styles''.
\end{description}

\subsubsection{Course title}
\begin{description}
\item [\joption{title=<title>}] Main title of the course
\item [\joption{titlesep=<separator>}] Separator between title and subtitle
\item [\joption{subtitle=<subtitle>}] Subtitle of the course
\item [\joption{shorttitle=<shorttitle>}] Short title of the course (for headings etc.)
\end{description}

\subsubsection{Date and place\label{sec:date-and-place}}
\begin{description}
\item [\joption{semester=<term>,}] where \joption{<term>} is one of

\begin{itemize}
\item \joption{fs}: Spring term (\emph{Frühjahrssemester}, short form: \emph{FS})
\item \joption{hs}: Fall term (\emph{Herbstsemester}, short form: \emph{HS})
\item \joption{ss}: Summer term (\emph{Sommersemester}, short form: \emph{SoSe})
\item \joption{ws}: Winter term (\emph{Wintersemester}, short form: \emph{WS})
\end{itemize}
Sec.~\ref{sec:customizing-strings} explains how to customize and extend this list.
Also cf. sec.~\ref{sec:styles}.

\item [\joption{year=<year>}] Year of the term
\item [\joption{uni=<university>}] Your university
\item [\joption{institute=<institute>}] Your institute/department
\item [\joption{room=<room>}] The room where the course generally takes place;
      it is possible to specify diverging rooms for individual sessions
      (see sec. \ref{sec:lecplan})
\item [\joption{startdate=<startdate>}] The date of the first session (the argument
      \emph{must} have the form DD/MM/YYYY); if no startdate is given,
      \jfcsmacro{today} is used
\item [\joption{interval=<interval>}] The interval (in days) between two sessions;
      the preset interval is 7 (=~weekly courses)
\end{description}

\subsubsection{Additional information}
\begin{description}
\item [\joption{instructor=<name>}] (General) course instructor's name;
      it is possible to specify different or specific instructors for individual sessions
      (see sec. \ref{sec:lecplan})
\item [\joption{shortinstructor=<name>}] Short form of the course instructor's name (e.\,g., for headings)
\item [\joption{platform=<data>}] Information of the e-learning platform
      (such as the URL)
\item [\joption{officehours=<data>}] Date of your office hours
\item [\joption{officenumber=<data>}] Your office (room) number
\end{description}

\subsubsection{Other global settings}
\begin{description}
	\item[\joption{sestitlesep=<separator>}] Specifies a default separator between session title and subtitle
\end{description}

\subsection{Via macros\label{sec:via-macros}}

The following macros provide an alternative way to set up the course metadata.

\subsubsection{Course classification}
\begin{itemize}
\item \jcsmacro{LecType\{<course type>\}}: Set course type;
\joption{<course type>} is one of\footnote{See above sec.~\ref{sec:lecture-classification} for a detailed
description.}

\begin{itemize}
\item \joption{vl}: Lecture (\emph{Vorlesung})
\item \joption{ps}: Undergraduate seminar (\emph{Proseminar})
\item \joption{se}: Seminar (\emph{Seminar})
\item \joption{ue}: Practical course (\emph{Übung})
\item \joption{ko}: Colloquium (\emph{Kolloquium})
\item \joption{pv}: Research seminar (\emph{Privatissimum})
\end{itemize}
\end{itemize}

\subsubsection{Course title}
\begin{itemize}
\item \jcsmacro{LecTitle[<package options>]\{<title>\}}: Record course title and options;
\joption{<package options>} might be any set of package options described
in sec.~\ref{sub:package-options}, so this macro can actually be used to record
all metadata.
\item \jcsmacro{LecTitleSep\{<title separator>\}}: Specify a separator between course
title and subtitle (e.\,g., ``. '' or `` -- '')
\item \jcsmacro{LecSubTitle\{<subtitle>\}}: Record course subtitle
\end{itemize}

\subsubsection{Date and place}
\begin{itemize}
\item \jcsmacro{LecYear\{<term>\}\{<year>\}}, Record term and
year of the course; \joption{<term>} is one of\footnote{See above sec.~\ref{sec:date-and-place} for a detailed
description.}

\begin{itemize}
\item \joption{fs}: Spring term (\emph{Frühjahrssemester})
\item \joption{hs}: Fall term (\emph{Herbstsemester})
\item \joption{ss}: Summer term (\emph{Sommersemester})
\item \joption{ws}: Winter term (\emph{Wintersemester})
\end{itemize}
\item \jcsmacro{LecUni\{<university>\}}: Record the name of
your university
\item \jcsmacro{LecInstitute\{<institute>\}}: Record your institute's/department's name
\item \jcsmacro{LecRoom\{<room>\}}: Record the room where the course (generally) takes place
\item \jcsmacro{LecStartDate\{<startdate>\}}: Set the date of
the first session (the argument \emph{must} have the form DD/MM/YYYY)
\item \jcsmacro{LecInterval\{<interval>\}}: Adjust the interval (in days) between two sessions.
      The preset interval is 7 (=~weekly courses).
\item \jcsmacro{SetAutoOffset\{<n>\}\{<days>\}}: Automatically shift all subsequent sessions
      by <days> extra  days after every <n>th session. This is useful if you have each week
      two regular sessions and then a pause until the next week (for instance, a Tuesday +
      Thursday course could be defined via \jcsmacro{LecInterval\{2\}} and 
      \jcsmacro{SetAutoOffset\{2\}\{3\}}). <n> must be a positive integer, <days> can 
      also be a negative integer value.
\end{itemize}

\subsubsection{Additional information}\label{ses-add}
\begin{itemize}
\item \jcsmacro{LecInstructor[<short name>]\{<name>\}}: Record the (general) instructor's name, including an optional short form for headings etc.
\item \jcsmacro{SetOfficeHours\{<office hours>\}}: Record date of your office hours
\item \jcsmacro{SetOfficeNumber\{<office number>\}}: Record your office (room) number
\item \jcsmacro{SetPlatform\{<platform information>\}}: Record information
(such as URL) of the e-learning platform
\end{itemize}

\subsubsection{Other global settings}\label{ses-global}
\begin{itemize}
\item \jcsmacro{SessionTitleSep\{<separator>\}}: Specify a default separator between session title and subtitle (e.\,g., ``. '' or `` -- ''). This is used if no specific separator has been specified in the session entry (see sec.~\ref{sec:lecplan}); by default, no separator is defined.
\end{itemize}

\section{Setting up a course schedule}\label{sec:lecplan}

In the metadata file, you can set up a schedule for the course by entering
session information in chronological order. This is done via the following
macro:
\begin{itemize}
\item \jcsmacro{NewSession[<options>]\{Session title\}}


Valid \joption{<options>} include:
\begin{itemize}
\item \joption{titlesep=<separator>}: Separator between session title and
    subtitle (e.\,g., \verb|titlesep={.\ }|); this overrides any global separator set via \joption{sestitlesep} option
    or \jcsmacro{SessionTitleSep} macro for the current session
\item \joption{subtitle=<subtitle>}: Subtitle of the session
\item \joption{shorttitle=<shorttitle>}: Short title (for
    headings etc.)
\item \joption{instructor=<name>}: Specific instructor for this session
    (if it differs from the usual course instructor)
\item \joption{shortinstructor=<name>}: Short form of the specific instructor for this session
\item \joption{presstudents=<names>}: Students presenting in this session
    (used for student presentation lists, see below sec.~\ref{sec:preslists})
\item \joption{room=<room>}: Room for this session (if it differs
    from the usual course room)
\item \joption{bibsec=<keyword>}: Session keyword for the bibliography
    (see below sec.~\ref{sub:bibliographies} for its use)
\item \joption{cancel=<true|false>}: Marks this session as ``canceled''.
    If you specify \joption{cancel=true}, the session will be printed
    in the program in bold type and appended by a verbal comment.
    For example,

\jcsmacro{NewSession[cancel=true]\{Dies Academicus\}}

will expand to
\begin{quote}
\textbf{15.\,05.: Dies Academicus -- keine Sitzung}
\end{quote}

(i.\,e., ``Dies Academicus -- no session'').

Furthermore, a canceled session is not counted in the session counter
that is used to retrieve session-specific information
(see below sec.~\ref{sec:session-specific-info}).

\end{itemize}
\item \jcsmacro{SetBreak[<span>]\{Break\}}: Add a semester break
(e.\,g., holidays) that affects one session. The macro increments
the internal counters respectively and expands in the program to

\begin{center}
\textbf{(Break)}
\par\end{center}

By means of the optional argument, the real time span of the break
might be given if you want to print it on the program. If you pass
an optional argument \joption{<span>}, the macro will expand to

\begin{center}
\textbf{(<span>: Break)}
\par\end{center}

So for instance, \jcsmacro{SetBreak[28.05.-{}-3.06.]\{Whitsun holidays\}}
expands to


\begin{center}
\textbf{(28.05.--3.06.: Whitsun holidays)}
\par\end{center}

\item \jcsmacro{SetBreaks[<options>]\{Break\}}: Add
a semester break that affects more than one session (e.\,g., two-week holidays).
The output in the program is identical to the \jcsmacro{SetBreak} macro,
but the counter incrementation can be adjusted to the needed time span.

Possible \jmacro{<options>} are:
\begin{itemize}
\item \joption{units=<n>}: Number of interval units the break takes. One \emph{unit}
    is the number of days as specified by the \joption{interval} option (one week by
    default\footnote{The former option \joption{weeks} is deprecated as of v. 0.9,
    since the interval can be adjusted now.}).
    This value is needed in order to increment the internal counter that is used to
    calculate the session dates. If \joption{units} is not specified, the counter is
    incremented by one.\footnote{That is: \jcsmacro{SetBreak\{Break\}} =
    \jcsmacro{SetBreaks\{Break\}} = \jcsmacro{SetBreaks[units=1]\{Break\}}.}
    <n> must be a positive integer.
\item \joption{span=<span>}: Real time span (verbally output on the program)
\end{itemize}
\item \jcsmacro{SetLecOffset\{<n>\}}: Shift the date of all subsequent sessions by <n> days.
    <n> can also be negative.
\item \jcsmacro{SetBeamerFrameBreak}: Add a frame break in
the beamer program at this position (more precisely, start a new frame).
This also increments the frame counter which is used for subsequent program
frame titles. Note that you can insert maximally 3 breaks.
\item \jcsmacro{SetBeamerHook\{<code>\}}: Add arbitrary LaTeX code to the
beamer program
\item \jcsmacro{begin\{SessionBlock\}\{<Block title>\}}\\
\ldots{} \\
\jcsmacro{end\{SessionBlock\}}:\\
Thematic block consisting of several sessions. Respective sessions
are nested inside this block.
\end{itemize}

\section{Retrieving general course information\label{sec:general-course-info}}

Once the metadata file is set up as documented above and input to
your document(s), you can retrieve the recorded as well as some concatenated
information by means the following macros.


\subsection{Course data}

The following macros output general course-specific information:
\begin{itemize}
\item \jcsmacro{lectype}: Outputs the course type in short
form (e.\,g., ``SE'')
\item \jcsmacro{lectypeverb}: Outputs the course type in
verbose form (e.\,g., ``Seminar'')
\item \jcsmacro{lectypesession}: Outputs the appropriate
``session'' string (e.\,g., ``Vorlesung'' or ``Sitzung'')
\item \jcsmacro{lectitle}: Outputs the main title of the
course
\item \jcsmacro{lectitlesep}: Outputs the separator between
title and subtitle
\item \jcsmacro{lecsubtitle}: Outputs the subtitle of the course
\item \jcsmacro{lecfulltitle}: Outputs the course's full title
    (title, separator, subtitle)
\item \jcsmacro{lecshorttitle}: Outputs the short version
of the course title; if no explicit short title is specified,
the normal title is output (you can check whether
there is a unique short title by the test
\jcsmacro{iftoggle\{uniquelecshorttitle\}\{<true>\}\{<false>\}})
\item \jcsmacro{lecsemshort}: Outputs the short version of
the term type (e.\,g., ``WS'')
\item \jcsmacro{lecsemverb}: Outputs the verbose version
of the term type (such as ``Winter\-semester'')
\item \jcsmacro{lecyear}: Outputs the year
\item \jcsmacro{lecsemester}: Outputs the short version of
the semester (e.\,g., ``WS 2014'')
\item \jcsmacro{lecsemesterverb}: Outputs the verbose version
of the semester (such as ``Winter\-semester 2014'')
\item \jcsmacro{lecuniversity}: Outputs the university's name
\item \jcsmacro{lecinstitute}: Outputs the institute's/department's name
\item \jcsmacro{lecinstructor}: Outputs the (general) instructor's name
\item \jcsmacro{lecshortinstructor}: Outputs short form of the (general) instructor's name;
if no explicit short name is given, the normal name will be output (you can check whether
there is a unique short name by the test
\jcsmacro{iftoggle\{uniquelecshortinstructor\}\{<true>\}\{<false>\}})
\item \jcsmacro{lecroom}: Outputs the (general) course room
\item \jcsmacro{lecplatform}: Outputs information on the
e-learning platform
\item \jcsmacro{officehours}: Outputs the office hours
\item \jcsmacro{officenumber}: Outputs the office (room) number
\end{itemize}

\subsection{Generating course programs}
\label{sec:lecprog}
\begin{itemize}
\item \jcsmacro{makeprogram}: Generates a course program in the form:


\begin{lstlisting}[language={[LaTeX]TeX},basicstyle={\small\ttfamily},frame=single]
\begin{labeling}{\lecprogramlistindent}
\item[<short date>] <session full title>
...
(break)
...
\item[<short date>] <session full title>
\end{labeling}
\end{lstlisting}



The \jmacro{labeling} environment is defined by the KOMA classes.
The package provides a fallback, however, if a different class is used.

\item \jcsmacro{makebeamerprogram[<options>]}: Generates
a beamer-suited lecture program from the metadata in the form


\begin{lstlisting}[language={[LaTeX]TeX},basicstyle={\small\ttfamily},frame=single]
\begin[label=beamerprogram<nr>,<bfoptions>]{frame}
\frametitle{<Heading>}
\begin{description}[\lecprogramlistindent]
\item[<short date>] <session full title>
...
(break)
...
\item[<short date>] <session full title>
\end{description}
\end{frame}
\end{lstlisting}



\joption{<options>} can be one of
\begin{itemize}
\item \joption{title=<title>}: Program title (<Heading>)
\item \joption{options=<bfoptions>}: Beamer frame options. Note that key-value
    beamer frame options need to be embraced, as in\\
    \jcsmacro{makebeamerprogram[options=\{shrink=10\}]}
\end{itemize}

Note that multiple subsequent frames are generated if the metadata
file contains \jcsmacro{SetBeamerFrameBreak} macros.
Also note that you can refer to the frames via the automatically generated
labels \emph{beamerprogram} (for the first frame), \emph{beamerprogram2}
for the second, etc. Finally note that the number of program frames
is currently limited to 4. If you need more, you should probably rethink
your program structure.

\end{itemize}

\subsection{Generating bibliographies\label{sub:bibliographies}}

The package provides macros for easy generation of sectioned bibliographies
via \textsf{biblatex}. The macro
\begin{itemize}
\item \jcsmacro{makesessionbib}
\end{itemize}
generates code in the form

\begin{lstlisting}[basicstyle={\small\ttfamily},frame=single,moretexcs={[1]{printbibliography}}]
\section{<session full title>}
\nocite{*}
\printbibliography[keyword=<session keyword>,heading=none]
\end{lstlisting}
 for each session of the lecture which has been linked to a \textsf{biblatex}
keyword via the \joption{bibsec} option (see above sec.~\ref{sec:lecplan}).

So if you specify your session with a keyword via the \joption{bibsec}
option, and tag your Bib\TeX{} database entries with that keyword,
you will get a list of session-specific literature.


\subsection{Generating student presentation lists}\label{sec:preslists}

The package provides macros to produce a list with the name of the students presenting
stuff, or generally being particularly involved, in specific sessions.

The names of the presenting students are assigned in the metadata to specific sessions
by means of the \joption{presstudents} option of the \jcsmacro{NewSession} command
(see above sec.~\ref{ses-add}). The macro

\begin{quote}
\jcsmacro{makepreslist}
\end{quote}
outputs a list that consists of the session dates and titles as well as the names of the
presenting students, i.\,e., it expands to code in the form:

\begin{lstlisting}[language={[LaTeX]TeX},basicstyle={\small\ttfamily},frame=single]
\begin{labeling}{\lecprogramlistindent}
\item[<short date>] <session full title>\par
                    <presenting students>
...
\end{labeling}
\end{lstlisting}
If no presenting students have been assigned to a given session,
an em-dash (---) is output instead.

A starred version of the macro outputs a ``blank'' presentation list that just consists of
the session dates and titles with enough space to fill in student names manually.
This version might be useful to schedule the presentations of your students in the first
session:

\begin{quote}
\jcsmacro{makepreslist*}
\end{quote}
For beamer presentations, finally, a specific macro

\begin{quote}
\jcsmacro{makebeamerpreslist}
\end{quote}
is provided (with no starred version). The main difference is the more compact design that makes
the list fit better on a slide.

If you want to start your presentation list only from a given session number (e.\,g., since you
do not have any presentations in the first session of the course), you can use

\begin{quote}
\jcsmacro{setfirstpressession\{<session number>\}}
\end{quote}
to set the first session number to be printed on the list. Likewise, 
\begin{quote}
\jcsmacro{setlastpressession\{<session number>\}}
\end{quote}
can be used to determine the last session number to be printed on the list.


\section{Retrieving session-specific information\label{sec:session-specific-info}}

In session-specific documents, you also need information specific
to the current session. This is done as follows.


\subsection{Setting the current session}

Use \jcsmacro{ThisSession\{<nr>\}} to tell the package
which session is current. \joption{<nr>} is an integer value, e.\,g.
\jcsmacro{ThisSession\{3\}} for the 3rd session of
the lecture.


\subsection{Generating session-specific information for the current session}

If you have specified the current session via the macro \jcsmacro{ThisSession},
the following macros output general session-specific information:
\begin{itemize}
\item \jcsmacro{sesdate}: Date of the current session
\item \jcsmacro{sesshortdate}: Date of the current session,
short form (no year)
\item \jcsmacro{sestitle}: Main title of the current session
\item \jcsmacro{sesshorttitle}: Short title of the current session; if
no explicit short title is specified, the normal [main] title is output
(you can check whether there is a unique short title by the test
\jcsmacro{iftoggle\{uniquesesshorttitle\}\{<true>\}\{<false>\}})
\item \jcsmacro{sestitlesep}: Title-subtitle separator of
the current session
\item \jcsmacro{sessubtitle}: Subtitle of the current session
\item \jcsmacro{sesfulltitle}: Full title of the current
session (title, separator, subtitle)
\item \jcsmacro{sesinstructor}: Current session's instructor's name; if you want to output this name only if it differs from the general instructor (\jcsmacro{lecinstructor}), use the starred version \jcsmacro{sesinstructor*} (furthermore, you can check whether
there is a unique session instructor by the test
\jcsmacro{iftoggle\{uniquesesinstructor\}\{<true>\}\{<false>\}})
\item \jcsmacro{sesshortinstructor}: Current session's instructor's short name; if you want to output this name only if it differs from the general instructor (\jcsmacro{lecshortinstructor}), use the starred version \jcsmacro{sesshortinstructor*}; if no explicit instructor short name is given, the normal instructor name will be output (you can check whether
there is a unique short instructor [that differs from the long session instructor name] by the test
\jcsmacro{iftoggle\{uniquesesshortinstructor\}\{<true>\}\{<false>\}})
\item \jcsmacro{sespresstudents}: Students presenting in this session
\item \jcsmacro{sesnr}: Number of the current session
\item \jcsmacro{sesroom}: Room of the current session
\end{itemize}

\subsection{Generating session-specific information for adjacent sessions}

Depending on the value of \jcsmacro{ThisSession}, you can retrieve the following
information for sessions that follow or precede the current session by a specific interval unit via the following macros:
\begin{itemize}
	\item \jcsmacro{AdjSessionTitle[<offset>]}: Outputs the main title
	of the adjacent session
	\item \jcsmacro{AdjSessionFullTitle[<offset>]}: Outputs the full
	title (main title, separator, subtitle) of the adjacent session
	\item \jcsmacro{AdjSessionShortTitle[<offset>]}: Outputs the short
	title of the adjacent session; if no explicit short title is specified, the normal main title is output
	\item \jcsmacro{AdjSessionDate[<offset>]}: Outputs the date of the adjacent session
	\item \jcsmacro{AdjSessionShortDate[<offset>]}: Outputs the short
	date (no year) of the adjacent session
	\item \jcsmacro{AdjSessionInstructor[<offset>]}: Outputs the name of the instructor of the adjacent session
	\item \jcsmacro{AdjSessionInstructor*[<offset>]}: Outputs the name of the instructor of the adjacent session if it differs from the general instructor (\jcsmacro{lecinstructor})
	\item \jcsmacro{AdjSessionShortInstructor[<offset>]}: Outputs the short name (or normal name, if no short name was specified) of the instructor of the adjacent session if it differs from the general instructor (\jcsmacro{lecshortinstructor})
	\item \jcsmacro{AdjSessionShortInstructor*[<offset>]}: Outputs the short name  (or normal name, if no short name was specified) of the instructor of the adjacent session
	\item \jcsmacro{AdjSessionPresStudents[<offset>]}: Outputs the name of the students presenting in the adjacent session
	\item \jcsmacro{AdjSessionRoom[<offset>]}: Outputs the room of the adjacent session
\end{itemize}
Via the numerical \joption{<offset>} option, you can specify which session, relative to the current one, you want to output. The default is \joption{1}, i.\,e., \jcsmacro{AdjSessionTitle} without argument outputs the title of the \emph{next} session. Negative values are valid: \jcsmacro{AdjSessionTitle[-1]}, thus, outputs the title of the \emph{previous} session.

\subsection{Generating session-specific information for an arbitrary session}

Independent of the value of \jcsmacro{ThisSession},
you can retrieve the following information for arbitrary sessions
(session number \joption{<nr>}) via the following macros:
\begin{itemize}
\item \jcsmacro{SessionTitle\{<nr>\}}: Outputs the main title
of session number \joption{<nr>}
\item \jcsmacro{SessionFullTitle\{<nr>\}}: Outputs the full
title (main title, separator, subtitle) of session number \joption{<nr>}
\item \jcsmacro{SessionShortTitle\{<nr>\}}: Outputs the short
title of session number \joption{<nr>}; if
no explicit short title is specified, the normal main title is output
\item \jcsmacro{SessionDate\{<nr>\}}: Outputs the date of
session number \joption{<nr>}
\item \jcsmacro{SessionShortDate\{<nr>\}}: Outputs the short
date (no year) of session number \joption{<nr>}
\item \jcsmacro{SessionInstructor\{<nr>\}}: Outputs the name of the instructor of session
number \joption{<nr>}
\item \jcsmacro{SessionInstructor*\{<nr>\}}: Outputs the name of the instructor of session
number \joption{<nr>} if it differs from the general instructor (\jcsmacro{lecinstructor})
\item \jcsmacro{SessionShortInstructor\{<nr>\}}: Outputs the short name (or normal name, if no short name was specified) of the instructor of session
number \joption{<nr>}
\item \jcsmacro{SessionShortInstructor*\{<nr>\}}: Outputs the short name  (or normal name, if no short name was specified) of the instructor of session
number \joption{<nr>} if it differs from the general instructor (\jcsmacro{lecinstructor})
\item \jcsmacro{SessionPresStudents\{<nr>\}}: Outputs the name of the students presenting
in session number \joption{<nr>}
\item \jcsmacro{SessionRoom\{<nr>\}}: Outputs the room of session number \joption{<nr>}
\item \jcsmacro{MakeProgramline\{<nr>\}}: Outputs a list
item line for session number \joption{<nr>} in the form

\begin{lstlisting}[language={[LaTeX]TeX},basicstyle={\small\ttfamily},frame=single]
\item[{\bfseries <short date>}] <session full title>
\end{lstlisting}

\end{itemize}

\section{Customizing the output}\label{sec:customizing-strings}


\subsection{Defining and customizing course types}

The following macro allows to define new course types and redefine existing ones:
\begin{itemize}
\item \jcsmacro{DefLecType\{<key>\}\{<short form>\}\{<title>\}\{<session title>\}}
\end{itemize}
A new type, say summer school, thus, could be defined as follows:
\begin{itemize}
\item \jcsmacro{DefLecType\{ss\}\{SS\}\{Summer School\}\{Session\}}
\end{itemize}
This could then be set via \jcsmacro{LecType\{ss\}} or the package option
\joption{type=ss}, respectively.

Likewise, you can use the macro to redefine existing styles, e.\,g. change
the ``session'' string of type \joption{vl} via
\begin{itemize}
\item \jcsmacro{DefLecType\{vl\}\{VL\}\{Vorlesung\}\{Einheit\}}
\end{itemize}
If you need to change or add types, consider the use of styles
(see sec.~\ref{sec:styles}).


\subsection{Defining and customizing term types}

The available term (semester) types can be changed and extended via the macro:
\begin{itemize}
\item \jcsmacro{DefSemType\{<key>\}\{<short form>\}\{<verbose form>\}}
\end{itemize}
Thus, you could add a new term type ``spring term'' via
\begin{itemize}
\item \jcsmacro{DefSemType\{st\}\{ST\}\{Spring Term\}}
\end{itemize}

\subsection{Customizing the date format}\label{sec:custdate}

If you need to change the date format, redefine the date styles \textsf{lecdate}
(for the long format) and \textsf{lecshortdate} (for the short format),
using the syntax provided by the \textsf{datetime2}
package. By default, the two formats are defined as follows:

\begin{lstlisting}[language={[LaTeX]TeX},basicstyle={\small\ttfamily},frame=single,moretexcs={[1]{DTMnewdatestyle}}]
\DTMnewdatestyle{lecdate}{% long date: DD.\,MM.~YYYY
\renewcommand*{\DTMdisplaydate}[4]{\DTMtwodigits{##3}.\,\DTMtwodigits{##2}.~##1}%
\renewcommand*{\DTMDisplaydate}{\DTMdisplaydate}%
}

\DTMnewdatestyle{lecshortdate}{% short date: DD.\,MM.
\renewcommand*{\DTMdisplaydate}[4]{\DTMtwodigits{##3}.\,\DTMtwodigits{##2}.}%
\renewcommand*{\DTMDisplaydate}{\DTMdisplaydate}%
}
\end{lstlisting}
\jfcsmacro{DTMtwodigits\{\#\#3\}} represents the day of the month (producing always two digits, i.\,e., \emph{01} not \emph{1}), \jfcsmacro{DTMtwodigits\{\#\#2\}} represents the month (also in two-digit form) and \jfmacro{\#\#1} represents the year. Please refer to the \textsf{datetime2} manual for details. 

If you want to redefine the styles, use \jfcsmacro{DTMrenewdatestyle} and change the definition accordingly. For instance, to get the typical American English date formats \emph{MM/DD/YYYY} and \emph{Month, DD}, redefine the formats as follows:

\begin{lstlisting}[language={[LaTeX]TeX},basicstyle={\small\ttfamily},frame=single,moretexcs={[1]{DTMrenewdatestyle}}]
\DTMrenewdatestyle{lecdate}{% long date: MM/DD/YYYY
\renewcommand*{\DTMdisplaydate}[4]{\DTMtwodigits{##2}/\DTMtwodigits{##3}/##1}%
}

\DTMrenewdatestyle{lecshortdate}{% short date: Month, DD
\renewcommand*{\DTMdisplaydate}[4]{\DTMenglishmonthname{##2}, ##3}%
}
\end{lstlisting}
Note that it is not necessary to include the \jfcsmacro{DTMDisplaydate} redefinition in the date format redefinition (since it does never change here). Note further that the macro \jfcsmacro{DTMenglishmonthname} used in the short date redefinition requires the \textsf{datetime2-english} module to be loaded (see \textsf{datetime2} manual for details).

Note, finally, that the date redefinition syntax used up to \jslp\ 1.2 is no longer supported, since it relied on the \textsf{datetime} package, which is deprecated (and superseded by \textsf{datetime2}). The \jslp\ package will issue a warning if you try to use the old syntax.


\subsection{Misc. customizing}

The canceling output is ``Session title -- keine <Session>'' (``keine''
is German for ``no''). To modify or translate this, redefine the
following macro

\begin{lstlisting}[language={[LaTeX]TeX},basicstyle={\small\ttfamily},frame=single]
\newcommand*\leccancel{\ -- keine \lectypesession}
\end{lstlisting}
The default program string used in beamer frames can be changed by
redefining

\begin{lstlisting}[language={[LaTeX]TeX},basicstyle={\small\ttfamily},frame=single]
\newcommand*\lecprogram{Programm}
\end{lstlisting}
The indentation used in program lists can be changed by redefining

\begin{lstlisting}[language={[LaTeX]TeX},basicstyle={\small\ttfamily},frame=single]
\newcommand*\lecprogramlistindent{\textbf{88.\,88.}}
\end{lstlisting}
Use \jfcsmacro{renewcommand{*}} for the redefinitions.


\subsection{Using styles}\label{sec:styles}

The most elegant way to do the customizing is to use \emph{lecture planner style} (*.lps) files.
These files can be loaded via the \joption{style=<style>} package option, where <style>
is the file name without *.lps extension.

Currently, the package ships three styles:
\begin{enumerate}
  \item \joption{german-default} simply includes the default strings.
     This style is meant to be used as a model for new styles.
  \item \joption{english} is a proof-of-concept localization to English.
     This style can be used as a basis for English styles. The English examples
     included in the \jslp\ bundle use this style.
  \item \joption{cologne} provides some specifics current at the University of Cologne
     (\emph{Universität zu Köln}):
     \begin{itemize}
      \item Additional course types: \joption{ak} (AK, \emph{Arbeitskurs}),
      \joption{as} (AS, \emph{Aufbauseminar}), \joption{es} (ES, \emph{Einführungsseminar}),
      \joption{evl} (EVL, \emph{Einführungsvorlesung}), \joption{hs} (HS, \emph{Hauptseminar}).
     \end{itemize}
     
\end{enumerate}
If you provide me with other style files, in particular
translations to other languages than German (but also other university conventions), I consider
them for inclusion to the package.

\clearpage

\part{Companion packages}

\section{The \jsmt\ package}

This section of the manual describes the user interface of the \jsmt\
package. Please also refer to the example files included in the bundle.

\subsection{Aim of this package}

This package provides a way to easily generate tables to track the members of a
university course (a table where you, or your students, can fill in names,
student IDs and e-mail adresses) and a table to record their presence,
should this be a requisite at your institute.

The package somewhat integrates with \jslp\ and can use the
metadata and styles of that package where necessary (see part~I of this
manual for details on metadata and styles).

Since the package was written for my own needs, the table design might not fit yours.
However, with some basic LaTeX knowledge, it should not be too hard to adapt it.
Like for \jslp, the default strings are German.
However, it is possible to customize and translate them.
This is described later in this manual.


\subsection{Requirements of \jsmt}\label{sec:req-jsmt} 

The following packages are required and loaded by \jsmt: 
\begin{itemize}
 \setlength\itemsep{2pt}
 \item \textsf{datatool} (only if the option \joption{datafile} is used)
 \item \textsf{ifthen}
 \item \textsf{calc}
 \item \textsf{longtable}
 \item \textsf{hhline}
 \item \textsf{xkeyval}
\end{itemize}
\jsmt\ can be used independently of
\jslp\ to some degree. The latter package is only required for specific
features (see below) and must be loaded explicitly in that case.

\subsection{Loading the package}

The package is loaded as usual:
\begin{quote}
\jcsmacro{usepackage[<options>]\{jsmembertable\}}
\end{quote}
Currently, the following package options are available:
\begin{itemize}
 \item \joption{datafile=<csv-file>}: Use external student data file (see sec.~\ref{sec:ext-data}).
 \item \joption{datakeys=<keyorder>}: Specify order of items in CSV data file (see sec.~\ref{sec:ext-data}).
\end{itemize}


\subsection{Loading external data}\label{sec:ext-data} 

Both course member and presence tables can be filled with external student data. To this end,
the package option \joption{datafile=<csv-file>} is provided. If it is used, the package tries
to access a comma-separated data file. Note that the external file must have the extension \emph{.csv},
and the extension must be omitted in the option, so
\begin{quote}
 \jcsmacro{usepackage[datafile=mystudents]\{jsmembertable\}}
\end{quote}
loads the file \texttt{mystudents.csv}.

It is assumed that the external CSV file conforms to the following structure:

\begin{lstlisting}[language={},basicstyle={\small\ttfamily},frame=single]
Prename1, Surname1, StudentID1, Email1
Prename2, Surname2, StudentID2, Email2
...
\end{lstlisting}
The order if items can be adjusted via the \joption{datakeys} package option.
The four items, \texttt{pname} (prename), \texttt{sname} (surname), \texttt{mid} (student ID) and \texttt{email}, can be freely re-ordered by that option. Note however, that all four items must be used. Thus, to change the order to \emph{Surname, Prename, Email, StudentID}, use:
\begin{quote}
	\jcsmacro{usepackage[datafile=mystudents,\\
	\hphantom{\textbackslash usepackage[}datakeys=\{sname,pname,email,mid\}]\{jsmembertable\}}
\end{quote}
Note, finally, that the CSV file should have the same encoding than the tex file.

\subsection{Generating a course member table}

In order to generate a course member table, simply insert

\begin{quote}
\jcsmacro{makemembertable\{<number of blank rows>\}}
\end{quote}
If an external data file has been loaded, \joption{<number of blank rows>} can either be empty or a positive
integer value. If no external data file has been loaded, \joption{<number of blank rows>} \emph{must} be a
positive integer value.

If no external data file has been loaded, the command generates a table with \joption{<number of blank rows>}
blank rows, to which your students can fill in their name, student ID and e-mail address.

If an external data file has been loaded, an appropriate number of rows is generated and the
respective student data is filled in. Additionally, \joption{<number of blank rows>} blank rows are
\emph{appended} after the filled-in rows (for the late birds that have not registered themselves yet).
If the command's argument is empty or \joption{0}, no extra rows are appended.

The number of columns of the member table is always 3, tracking \emph{student id},
\emph{name} and \emph{e-mail address}.
If you want to have more or less columns, you need to redefine the
\jcsmacro{makemembertable} command.
The header strings, though, can easily be changed by redefining the following three
macros (using \jfcsmacro{renewcommand*}), for instance like this:

\begin{lstlisting}[language={[LaTeX]TeX},basicstyle={\small\ttfamily},frame=single]
% Student Name
\renewcommand*\jsmnameheader{\textbf{Student name}}
% Student ID
\renewcommand*\jsmidheader{\textbf{Student ID}}
% Email
\renewcommand*\jsemailheader{\textbf{Email address}}
\end{lstlisting}
If you use the \jslp\ package, you can use the \jslp\
style files in order to store those redefinitions globally.
See the \texttt{german-default.lps} style file for a model.\footnote{%
Note that within styles, you must use \jfcsmacro{newcommand*} instead of
\jfcsmacro{renewcommand*}, since the styles are loaded before the \jsmt\ package.}
Of course, you need to load \jslp\ with the respective \joption{style} option then
(\emph{before} \jsmt).
See above section~\ref{sec:styles} for details on styles.

\subsection{Generating a presence table}

Presence tables consist of rows with your students' names and columns for each session
of your course where each student can sign and mark her/his presence in the respective
session. As with the member tables, the package can fill in student data (the student
name in this case) from an external data file if the \joption{datafile} package option
is used.

The package provides two kinds of presence tables: A presence table with real session dates
and a simpler one just with session numbers (``Session~1'' etc.). The first variant requires
the \jslp\ package, since it uses the course metadata in order to generate a matching number
of columns with the respective session date in the column headers. The second one also works
without \jslp\, since the session numbers can be simply derived from an internal counter and
you can manually set the total number of sessions.

Note that if you use \jslp, you must load the \jslp\ package and also input the metadata file
\emph{before} \jsmt.

The first presence table variant (with real session dates) is produced with the following macro:

\begin{quote}
\jcsmacro{makeprestable\{<number of blank rows>\}}
\end{quote}
As with the member table, an appropriate number of rows, pre-filled with student data, is
generated if an external data file has been loaded. Then, \joption{<number of blank rows>}
blank rows are \emph{appended} after the filled-in rows (if \joption{<number of blank rows>}
is not empty or \joption{0}). If no external data file has been loaded, simply a table with
\joption{<number of blank rows>} blank rows is constructed.

The number of columns/sessions is automatically calculated from the metadata. If you want a different
number, you can use the optional argument of the command to override this calculation:

\begin{quote}
\jcsmacro{makeprestable[<number of sessions>]\{<number of blank rows>\}}
\end{quote}
The second kind of presence table (with session numbers instead of session dates) is provided
via the starred version of the command:

\begin{quote}
\jcsmacro{makeprestable*[<number of sessions>]\{<number of blank rows>\}}
\end{quote}
Like with the unstarred version, if the \jslp\
metadata is used/available, the number of columns/sessions is calculated from the metadata.
Again, the optional argument can be used to override this calculation.
If the \jslp\ metadata is not used/available, and no session number is given via the optional
argument, the table will use a preset number of sessions, namely 15. The starred version uses,
like the unstarred variant, the external student data if the \joption{datafile} option has been
used.

For courses of 2--16 sessions, the package tries to produce reasonably sized tables that
fit the page width (more than 16 sessions are currently not supported).
From 7 sessions upwards, two separate tables, each for half a term,
are produced. In general, it is assumed that you use landscape page format for presence tables.
The tables will be too wide for portrait page format. Also, the tables have been optimized for A4
page size.

The header strings of the presence tables can be adjusted by redefining the following
macros (using \jfcsmacro{renewcommand*}), for instance like this:

\begin{lstlisting}[language={[LaTeX]TeX},basicstyle={\small\ttfamily},frame=single]
% Student Name
\renewcommand*\jsmnameheader{\textbf{Student name}}
% "Session" string for the starred macro version
\renewcommand*\jsmsession{Session}}
% Session header for the starred macro version
% (\thesession outputs the counter value)
\renewcommand*\jsmsessionheader{\textbf{\jsmsession\ \thesession}}
% The advice for students to sign
\renewcommand*\jssigheader{Students' signature}
\end{lstlisting}
Again, if you use \jslp, you can use the \jslp\
style files in order to store those redefinitions globally.
See the \texttt{german-default.lps} and \texttt{english.lps} style files for a model.\footnote{%
Note that within styles, you must use \jfcsmacro{newcommand*} instead of
\jfcsmacro{renewcommand*}, since the styles are loaded before the \jsmt\ package.}
Of course, you need to load \jslp\ with the respective \joption{style} option then
(\emph{before} \jsmt).
See above section~\ref{sec:styles} for details on styles.

Note, furthermore, that the ``Session'' string (value of \jcsmacro{jsmsession}) is by default
linked to \jslp's \jcsmacro{lectypesession} value if 
\jslp\ is loaded before \jsmt. So if \jcsmacro{lectypesession} fits, you do not have to redefine
\jcsmacro{jsmsession}.


\clearpage

\appendix

\part{Appendix}

\section{Acknowledgements}

I could not have written the packages of the \jslp\ bundle without the expertise of the incredible \LaTeX\
community. The packages heavily rely on functions and features
provided by other packages (which are listed in sec.~\ref{sec:req-jslp} and \ref{sec:req-jsmt}).
I am deeply indepted to the authors of those packages.
Furthermore, \emph{stackexchange} proved to be a great source of knowledge which
provided me with solutions for specific tasks:
\jsmt\ heavily draws on code for dynamic table generation that has been
provided by Herbert Voss (\url{http://tex.stackexchange.com/a/7594}); \jslp\ and \jsmt\
use code to test for \jfcsmacro{romannumeral} arguments which has been taken from
a \emph{stackexchange} post by Enrico Gregorio (\url{http://tex.stackexchange.com/a/50131}).
Thank you, Herbert and Enrico! Finally, Dominik Waßenhoven tested the package and provided
me with multiple suggestions, which effectively manifested in major new features such as
the \jslp\ style files. Thanks, Dominik.

\section{Release History}

\begin{itemize}
\item 2017/03/12 (v. 1.5):
	\begin{itemize}
		\item Add \joption{english} style file (proof of concept).
		\item Add \joption{datakeys} option to \jsmt.
		\item Add package option \joption{sestitlesep} and macro \jcsmacro{SessionTitleSep} that
		allow for the definition of a global session title-subtitle	separator.
	\end{itemize}
\item 2016/10/19 (v. 1.4):
	\begin{itemize}
		\item Add instructor short forms for lecture and session.
		\item Add starred versions of the \jcsmacro{sesinstructor}, \jcsmacro{SessionInstructor} and \jcsmacro{AdjSessionInstructor} macros that only produce output if the session instructor differs from the general course instructor.
		\item All short\{instructor|title\} macros now output the long version if no short form was defined.
		\item Add boolean tests for unique short forms and session instructors.
	\end{itemize}
\item 2016/08/31 (v. 1.3):
     \begin{itemize}
     	\item \textbf{Backwards-incompatible change!} Use \textsf{datetime2} instead of \textsf{datetime} and \textsf{advdate}.
     	      This changes the interface to set the lecture date format. See sec.~\ref{sec:custdate}.
     	\item Fix output of \jcsmacro{SetBreaks} when no \joption{span} argument is given.
     	\item Protect content of some \jcsmacro{Lec}* macros and options to allow for commas in
     	      titles etc.
        \item Microtypographic improvement in default definition of the lecture date format.
	 \end{itemize}
\item 2016/05/11 (v. 1.2):
    \begin{itemize}	
	\item Fix line breaking with empty session titles before course breaks. 
	\item New commands for getting adjacent session data:
	   \begin{itemize}	
		  \item \jcsmacro{AdjSessionFullTitle}
		  \item \jcsmacro{AdjSessionDate}
		  \item \jcsmacro{AdjSessionShortTitle}
		  \item \jcsmacro{AdjSessionTitle}
		  \item \jcsmacro{AdjSessionShortDate}
		  \item \jcsmacro{AdjSessionRoom}
		  \item \jcsmacro{AdjSessionInstructor}\enlargethispage{\baselineskip}
		  \item \jcsmacro{AdjSessionPresStudents}
	  \end{itemize}
    \end{itemize}
\item 2015/07/15 (v. 1.1):
     \begin{itemize}
       \item Include and document the \jsmt\ package.
       \item Add support for student presentation lists. This introduces the new macros
             \jcsmacro{makepreslist}, \jcsmacro{makepreslist*},
             \jcsmacro{makebeamerpreslist}, \jcsmacro{setfirstpressession} and
             \jcsmacro{setlastpressession}.
       \item Major revision of the manual.
     \end{itemize}
\item 2015/07/07 (v. 1.0.2):
     \begin{itemize}
       \item Permit \jcsmacro{LecType} and \jcsmacro{LecYear} in the document body again
             (fix a regression introduced by v. 1.0).
     \end{itemize}
\item 2015/02/27 (v.\,1.0.1):
     \begin{itemize}
       \item Properly expand \jcsmacro{leccancel}
             (fix a regression introduced by v. 1.0).
     \end{itemize}
\item 2015/02/27 (v.\,1.0):
     \begin{itemize}
       \item Lecture types and term types are not hardcoded anymore and can be freely
             modified and extended via \jcsmacro{DefLecType} and \jcsmacro{DefSemType}.
       \item Add option to add the instructor's name to both the course (via macro
             \jcsmacro{LecInstructor} or \joption{instructor} package option) and
             to specific sessions (via \joption{instructor} option of
             \jcsmacro{NewSession}).
       \item Add option to add names of presenting students to a session (via option
             \joption{presstudents}).
       \item Add option to record the office number (\jcsmacro{SetOfficeNumber}
             or package option \joption{officenumber}).
       \item Fix expansion issue in \joption{options} option of \jcsmacro{makebeamerprogram}.
       \item Add option to automatically shift all subsequent sessions by a certain value
             after every \emph{n}th session (\jcsmacro{SetAutoOffset}).
       \item Add \joption{cologne} style file (suggested by Dominik Waßenhoven).
    \end{itemize}
\item 2015/02/08 (v. 0.9):
     \begin{itemize}
       \item Add a way to adjust the interval between two sessions
             (\joption{interval} package option and \jcsmacro{LecInterval} macro).
       \item Add a way to shift session dates from the regular interval
             (by means of macro \jcsmacro{SetLecOffset}).
       \item Add option and macro to set a room for the course as well as
             a session-specific room.
       \item Rename option \joption{weeks} of the \jcsmacro{SetBreaks} macro
             to \joption{units} (\joption{weeks} still works, but is marked deprecated).
    \end{itemize} 
\item 2015/01/17 (v.\,0.8):
    \begin{itemize}
       \item Fix corruption of \jfcsmacro{today}.
       \item Add framework for different styles.
       \item Add option and macro to set a room for the course as well as
             a session-specific room.
       \item Remove redundant lecture type \joption{vo} from the documentation.
       \item Change \jcsmacro{leccancel} default definition in favour of better
             translatability.
    \end{itemize}\filbreak
\item 2015/01/04 (v.\,0.7):
    \begin{itemize}
       \item Add macro for resetting \jfcsmacro{today}.
       \item Minor corrections of the manual.
    \end{itemize}
\item 2014/12/12 (v.\,0.6\,b): Minor corrections of the manual and example files.
\item 2014/12/12 (v.\,0.6): Initial release to CTAN.
\end{itemize}

\end{document}
